|

### 2020-12-06 appendix/appendix.Rmd
more edits to appendix, change font tikz2pdf

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

[^freire]: Independent Researcher, <danilofreire@brown.edu>, <http://danilofreire.github.io>. Corresponding author.

@@

## Lower House Size and Log of Expenditure per Capita (RDD Only)

@@

mod5_permu %>%
  select(-model) %>%
  kable(booktabs = T,align = "c",linesep ='') %>%
  kable_styling(c("striped","bordered","scale_down"), position = "center")
```

@@

```{r, warning=F, error=F, message=F, cache=T}
coefs <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV",
          "Method: RDD"))

aux <- list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model))
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
  filter(` ` != "Method: RDD") %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*",
                                     ifelse(. >= 0.05, " ",
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~(ifelse(is.na(.), " ", .)))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model))
  }) %>%
  reduce(bind_cols) %>%
  mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*",
                                     ifelse(. >= 0.05, " ",
                                            ifelse(is.na(.), " ", .))))))))) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2)
```

# Robustness: Meta-Regressions with Our Complete Sample

>>>>

---
title: |
       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
author:
- "Huzeyfe Alptekin[^alptekin]"
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "Catarina Roman[^roman]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 11pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.

@@

## Lower House Size and Log of Expenditure per Capita (RDD)

@@

mod5_permu %>%
  select(-model) %>%
  kable(booktabs = T,align = "c",linesep ='') %>%
  kable_styling(c("striped","bordered"), position = "center")
```

@@

# Robustness: Meta-Regressions (All Coefficients)
